Multisensor Architecture for an Intersection Management System

### 2015-06-10 ch2-mdf_ims.tex
Update reference to table and added caption and label

In the proposed work, there is not a deployment of sensors in an intersection scenario, but datasets from the previous mentioned projects will be used instead. Also, one of the objectives is to explore and propose a modular fusion architecture/framework for IMS based on cameras and laser sensors. In table X a summary of aforementioned developments is presented, including proposed work.

\begin{table}
\begin{tabular}{|c|c|p{0.125\linewidth}|p{0.15\linewidth}|c|c|c|c|}
\hline

@@

Proposed work & - & Lasers, Cameras & Vehicles & Multilevel & Yes \\
\hline

\end{tabular}
\end{table}

>>>>

In the proposed work, there is not a deployment of sensors in an intersection scenario, but datasets from the previous mentioned projects will be used instead. Also, one of the objectives is to explore and propose a modular fusion architecture/framework for IMS based on cameras and laser sensors. In table \ref{summary_FusIMS} a summary of aforementioned developments is presented, including proposed work.

\begin{table}[!t]
\begin{tabular}{|c|c|p{0.125\linewidth}|p{0.15\linewidth}|c|c|c|c|}
\hline

@@

\textbf{Proposed work} & - & \textbf{Lasers, Cameras} & \textbf{Vehicles} & \textbf{Yes} & \textbf{Yes} \\
\hline

\end{tabular}
\caption{Summary of recent developments involving sensor fusion for Intersection Management Systems}
\label{summary_FusIMS}
\end{table}
